The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-12 rockerverse.tex
update tex file

@@

run any container, the package \CRANpkg{googleCloudRunner}
\citep{cran:googleCloudRunner} demonstrates how R can be used as the
control language for one-time or batch processing jobs and scheduling of

>>>>

\textbf{\CRANpkg{googleCloudRunner}} is an interface with
\href{https://cloud.google.com/}{Google Cloud Platform}
container-related services, with tools to make it easier for R users to
interact with them for common use cases \citep{cran:googleCloudRunner}.
It includes deployment functions for creating R APIs using the
Docker-based \href{https://cloud.run}{Cloud Run} service. Users can
create long running batch jobs calling any Docker image including Rocker
via \href{https://cloud.google.com/cloud-build/}{Cloud Build} and
schedule services using \href{https://cloud.google.com/scheduler/}{Cloud
Scheduler}.

@@

run any container, the package \pkg{googleCloudRunner} demonstrates how
R can be used as the control language for one-time or batch processing
jobs and scheduling of
